---
title: "Diagnostics and Sensitivity of Stock Synthesis"

author: 
 - Max Cardinale (SLU) 
 - Henning Winker (GFCM)
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    number_sections: yes
    #toc: yes
    #keep_tex: false
vignette: >
  %\VignetteIndexEntry{ss3daigs Vignetted}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r wrap-hook, echo = FALSE}
library(knitr)
hook_output = knit_hooks$get('output')
knit_hooks$set(output = function(x, options) {
  # this hook is used only when the linewidth option is not NULL
  if (!is.null(n <- options$linewidth)) {
    x = knitr:::split_lines(x)
    # any lines wider than n should be wrapped
    if (any(nchar(x) > n)) x = strwrap(x, width = n)
    x = paste(x, collapse = '\n')
  }
  hook_output(x, options)
})
```


```{r, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "  " ,fig.align = 'center', cache=FALSE,tidy.opts=list(width.cutoff=80), tidy=TRUE)

```

## Load packages

```{r, message=FALSE}
# Load
library(r4ss)
library(ss3diags)
library(mvtnorm)
library(FLCore)
library(ggplotFL)
library(kobe)
require(plyr)
require(dplyr)
require(reshape2)
library(grid)
library(png)

```

# Central Baltic herring ensemble 

All models are annual, one sex, one fleet and with one acoustic survey

The $B_{MSY}$ proxy is set to 35\%$SSB_0$ with a corresponding $F_{SB35}$

+ *Run1* reference run, average M
+ *Run2* Low M
+ *Run3* High M
+ *Run4* High M (placeholder for testing) 

```{r}

scenarios = c("Run1","Run2","Run3","Run4") 

```

## Load runs

Define folder with R data files

```{r}
rdata = "rdata_runs"
runs = list.files(rdata)
```

Get list of rdata files

```{r}
mods = list()
for(i in 1:length(runs)){
  load(file.path(rdata,runs[i]))
  mods[[i]] = ss3rep
}
mods= mods[c(1,3,2,4)]
names(mods) = scenarios
```

# Selected Model Diagnostics

More computational intense model diagnostic were run for 3 selected runs:

+ *Run1* reference run, average M
+ *Run2* Low M
+ *Run3* High M
+ *Run4* High M (placeholder for testing) 

Select the runs used for diagnostics

```{r}
dm = mods[c(1,2,3,4)]

```

Load retro data

```{r}
rdata = "rdata_retros"
runs = list.files(rdata)
retros = list()
for(i in 1:length(runs)){
  load(file.path(rdata,runs[i]))
  retros[[i]] = retroModels
}

hcs = retros[c(1,2,3,4)]
names(hcs) = names(dm)
```

Make list of hindcast trends form retrospective runs

```{r}

hc = lapply(hcs,function(x){
  hci = r4ss::SSsummarize(x,verbose=F)
  hci
  })

```

Compile length comps from retrospective runs


```{r}

hc.age = lapply(hcs,function(x){
  hcl = ss3diags::SSretroComps(x)
  hcl
  })


```

## Goodness of Fits

### Indices

```{r fit1, fig.height=8,fig.width=10, fig.cap = paste0("Index residual plots for the acoustic survey index with trends indicating the trends for four scenarios")}
sspar(mfrow=c(2,2),plot.cex = 0.9)
SSplotJABBAres(dm[[1]],add=T,verbose = F)
legend("topleft","Run1",cex=1.3)
SSplotJABBAres(dm[[2]],add=T,verbose = F)
legend("topleft","Run2",cex=1.3)
SSplotJABBAres(dm[[3]],add=T,verbose = F)
legend("topleft","Run3",cex=1.3)
SSplotJABBAres(dm[[4]],add=T,verbose = F)
legend("topleft","Run4",cex=1.3)

```

```{r fit2, fig.height=8,fig.width=10, fig.cap = paste0("Index residual runs tests for the acoustic survey index with trends indicating the trends for four scenarios")}
sspar(mfrow=c(2,2),plot.cex = 0.9)
SSplotRunstest(dm[[1]],add=T,verbose = F)
legend("topleft","Run1",cex=1.3)
SSplotRunstest(dm[[2]],add=T,verbose = F)
legend("topleft","Run2",cex=1.3)
SSplotRunstest(dm[[3]],add=T,verbose = F)
legend("topleft","Run3",cex=1.3)
SSplotRunstest(dm[[4]],add=T,verbose = F)
legend("topleft","Run4",cex=1.2)


```

\newpage

### Size Composition Data

```{r fit3, fig.height=8,fig.width=10, fig.cap = paste0("Index residual plots for the mean age with trends indicating the trends for four scenarios")}
sspar(mfrow=c(2,2),plot.cex = 0.9)
SSplotJABBAres(dm[[1]],add=T,subplots = "age",verbose = F)
legend("topleft","Run1",cex=1.3)
SSplotJABBAres(dm[[2]],add=T,subplots = "age",verbose = F)
legend("topleft","Run2",cex=1.3)
SSplotJABBAres(dm[[3]],add=T,subplots = "age",verbose = F)
legend("topleft","Run3",cex=1.3)
SSplotJABBAres(dm[[4]],add=T,subplots = "age",verbose = F)
legend("topleft","Run4",cex=1.3)

```

\newpage

### Run1

```{r len1, fig.height=8,fig.width=10, fig.cap = paste0("Residual runs tests on mean lengths for the Run1")}
i=1
sspar(mfrow=c(2,2),plot.cex = 0.65)
SSplotRunstest(dm[[i]],add=T,subplots="age",verbose=F)

```

\newpage

### Run2

```{r len2, fig.height=8,fig.width=10, fig.cap = paste0("Residual runs tests on mean age for the Run2")}
# Retro
i=2
sspar(mfrow=c(2,2),plot.cex = 0.65)
SSplotRunstest(dm[[i]],add=T,subplots="age",verbose=F)

```

\newpage

### Run3

```{r len3, fig.height=8,fig.width=10, fig.cap = paste0("Residual runs tests on mean age for the Run3")}

i=3
sspar(mfrow=c(2,2),plot.cex = 0.65)
SSplotRunstest(dm[[i]],add=T,subplots="age",verbose=F)

```

\newpage

### Run4

```{r len4, fig.height=8,fig.width=10, fig.cap = paste0("Residual runs tests on mean age for the Run4")}
i=4
sspar(mfrow=c(2,2),plot.cex = 0.65)
SSplotRunstest(dm[[i]],add=T,subplots="age",verbose=F)

```

\newpage

## Retrospective Analysis

### Run1

```{r ret1, fig.height=8,fig.width=10, fig.cap = paste0("Retrospective analysis and retrospective forecasts for the Run1")}
# Retro
i = 1
sspar(mfrow=c(2,2),plot.cex = 0.65)
SSplotRetro(hc[[i]],add=T,legend=F,forecast=F,verbose = F)
SSplotRetro(hc[[i]],add=T,forecastrho = T,legend=F,verbose = F)
SSplotRetro(hc[[i]],subplots = "F",add=T,legend=F,forecast=F,
            verbose = F)
SSplotRetro(hc[[i]],subplots = "F",add=T,forecastrho = T,legend=F,
            verbose = F)
mtext(c("Retro","Forecast"),3,outer=T,line=-0.5,at=c(0.3,0.8),cex=0.8)

```


\newpage

### Run2 

```{r ret2, fig.height=8,fig.width=10, fig.cap = paste0("Retrospective analysis and retrospective forecasts for the Run2")}
# Retro
i = 2
sspar(mfrow=c(2,2),plot.cex = 0.65)
SSplotRetro(hc[[i]],add=T,legend=F,forecast=F,verbose = F)
SSplotRetro(hc[[i]],add=T,forecastrho = T,legend=F,verbose = F)
SSplotRetro(hc[[i]],subplots = "F",add=T,legend=F,
            forecast=F,verbose = F)
SSplotRetro(hc[[i]],subplots = "F",add=T,
            forecastrho = T,legend=F,verbose = F)
mtext(c("Retro","Forecast"),3,outer=T,line=-0.5,at=c(0.3,0.8),cex=0.8)

```


\newpage

### Run3


```{r ret3, fig.height=8,fig.width=10, fig.cap = paste0("Retrospective analysis and retrospective forecasts for the Run3")}
# Retro
i = 3
sspar(mfrow=c(2,2),plot.cex = 0.65)
SSplotRetro(hc[[i]],add=T,legend=F,forecast=F)
SSplotRetro(hc[[i]],add=T,forecastrho = T,legend=F)
SSplotRetro(hc[[i]],subplots = "F",add=T,legend=F,forecast=F)
SSplotRetro(hc[[i]],subplots = "F",add=T,forecastrho = T,legend=F)
mtext(c("Retro","Forecast"),3,outer=T,line=-0.5,at=c(0.3,0.8),cex=0.8)

```

\newpage

### Run4

```{r ret4, fig.height=8,fig.width=10, fig.cap = paste0("Retrospective analysis and retrospective forecasts for the Run4")}
# Retro
i = 4
sspar(mfrow=c(2,2),plot.cex = 0.65)
SSplotRetro(hc[[i]],add=T,legend=F,forecast=F)
SSplotRetro(hc[[i]],add=T,forecastrho = T,legend=F)
SSplotRetro(hc[[i]],subplots = "F",add=T,legend=F,forecast=F)
SSplotRetro(hc[[i]],subplots = "F",add=T,forecastrho = T,legend=F)
mtext(c("Retro","Forecast"),3,outer=T,line=-0.5,at=c(0.3,0.8),cex=0.8)

```


\newpage

## Hindcasting Cross-Validation

### Indices

```{r hc1, fig.height=8,fig.width=10, fig.cap = paste0("Hindcast cross-validations for the acoustic survey Indices")}
sspar(mfrow=c(2,2),plot.cex = 0.9)
SSplotHCxval(hc[[1]],add=T,verbose = FALSE)
legend("topleft","Ref",cex=1.3)
SSplotHCxval(hc[[2]],add=T,verbose = FALSE)
legend("topleft","MK",cex=1.3)
SSplotHCxval(hc[[3]],add=T,verbose = FALSE)
legend("topleft","MK.FL",cex=1.3)
SSplotHCxval(hc[[4]],add=T,verbose = FALSE)
legend("topleft","MK.lh",cex=1.2)


```

\newpage


# Sensitivities



Get the labels for the Bratio and Fratio

```{r}
mvn=SSdeltaMVLN(mods[[3]],Fref="Btgt",mc=2,plot=F)
mvn$labels
```
Create uncertainty with delta-MVLN approximation 

```{r}
kbs = NULL
# Compare indices
for(i in 1:length(scenarios)){
  kbs = rbind(kbs,SSdeltaMVLN(mods[[i]],
          run=scenarios[i],Fref="Btgt",
          plot=F,verbose = F,years=1903:2020)$kb)
}
```


```{r fig1, fig.height=9,fig.width=8, fig.cap = paste0("Comparison of stock trajectories")}

sspar(mfrow=c(3,2),plot.cex = 0.7)
SSplotEnsemble(kbs,
               uncertainty =F,
               add=T,ylabs=mvn$labels,
               legendcex = 0.65,
               legendloc = "topright",verbose = F)

```


```{r fig2, fig.height=9,fig.width=8, fig.cap = paste0("Comparison of stock trajectories with 95\\% CIs")}

sspar(mfrow=c(3,2),plot.cex = 0.7)
SSplotEnsemble(kbs,
               uncertainty =T,
               add=T,ylabs=mvn$labels,
               legendcex = 0.65,
               legendloc = "topright",verbose = F)

```

```{r,warning=F}
get_plot = "Compare.png"

# By run
Par = list(mfrow=c(1,1),mar = c(5, 5, 1, 1), mgp =c(3,1,0), tck = -0.02,cex=0.8)
png(file = get_plot, width = 6.5, height = 5.5, 
    res = 200, units = "in")
par(Par)
kbp = kobe:::kobePhaseMar2(
  transform(kbs[kbs$year==2020,],
  run=paste(run))[,c("stock","harvest","run")],
  xlab = expression(B/B[tgt]),
  ylab =expression(F/F[tgt]),
  ylim =5,xlim=3,col=rainbow(7)[3:7],
  quadcol=c("red","green","yellow","orange"))

dev.off()
```

```{r fig3, fig.height=7,fig.width=8, fig.cap = paste0("Kobe plot showing the comparison of stock status posteriors for 2020 with marginal posterior distributions")}


# Beautify
DIMs=c(6,5.5)
# setup plot
par(mar=rep(0,4),omi= c(0, 0, 0, 0)) # no margins

# layout the plots into a matrix w/ 12 columns, by row
layout(matrix(1:1, ncol=1, byrow=TRUE))

# example image
img <- readPNG(paste0(get_plot))

# do the plotting
plot(NA,xlim=0:1,ylim=0:1,
     xaxt="n",yaxt="n",bty="n")

rasterImage(img,0,0,1,1)
legend("topright",scenarios,pch=22, pt.bg=rainbow(7)[3:7],box.lty = 0, cex=1.2)

```

\newpage

